---
title: "RmdUfosightings"
author: "Thomas Maher"
date: "August 19, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Rufosightings

The best part of the Rufosightings R package is the report itself, found here **Rufosightings$description**.  Even so, the other columns can reveal other details of interest. 

```{r echo = FALSE, message = FALSE, warning = FALSE}
library(devtools)
```

We will make plots with the Rufosightings package. 

```{r echo = FALSE, message = FALSE, warning = FALSE}
install_github("botanyhelp/Rufosightings")
library(Rufosightings)
```

## Visualizing UFO Sightings

### Shape of Flying Object

We can see that these shapes of UFO are the most frequently reported:

* light
* triangle
* unknown
* disk
* circle

```{r echo=FALSE}
barplot(table(Rufosightings$shape),horiz = T,las=1, col=c(rainbow(length(levels(Rufosightings$shape)))) )
```

We can also see that the construction of the data frame has some quality control problems. 

### Month of Year

We can see that the northern hemisphere's summer months tend to show the highest number of reports

```{r echo=FALSE}
barplot(table(Rufosightings$sighted_at_month),horiz = T,las=1)
```

### Day of Month

We can see that the 1st and 15th of the month is over represented. The 4th of July might give a bump and new years day might improve the numbers for the 1st day.

```{r echo=FALSE}
barplot(table(Rufosightings$sighted_at_day),horiz = T,las=1 )
```

### 